### 2015-12-02 paper.tex
Comment on turbine orientation in mean velocity fig

\begin{figure}[h]
\includegraphics[width=\textwidth]{figures/meancontquiv}
\caption{{\bf Mean Velocity.}
Mean velocity field at 1 m downstream ($x/D=0.93$), $U_\infty=1.0$ m/s, and
$\lambda=3.1$.}\textbf{\textit{[is this looking downstream or upstream? may want to indicate the rotation direction of the downstream rotor side ( right or left)]}}
\label{fig:meancontquiv}
\end{figure}

>>>>

\begin{figure}[h]
    \includegraphics[width=\textwidth]{figures/meancontquiv}

    \caption{{\bf Mean Velocity.}Mean velocity field (looking upstream) at 1 m
    downstream ($x/D=0.93$), $U_\infty=1.0$ m/s, and $\lambda=3.1$. Refer to
    Fig.~\ref{fig:coordinates} for turbine axis orientation.}

    \label{fig:meancontquiv}
\end{figure}
